\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-07 doc/paper.tex
extended conclusions.

We presented \fs, a Mathematica package, which generates fast and
modular spectrum generators for non-minimal SUSY models.  It comes
with plenty of predefined models for the CMSSM, NMSSM, USSM, \ESSM,
MRSSM etc., which can be generated immediately without any editing.
In particular the CMSSM and NMSSM spectrum generators constitute
alternatives to the existing ones Softsusy, SPheno and NMSPEC.  We
have shown that the generated source code can be influenced at two
different levels: The \mathematica level where the user provides a
model file, and the C++ level where the generated objects can be
easily exchanged, extended, modified and reused.  This provides great
flexibility for creating custom spectrum generators for both the most
common and most extraordinary models.

>>>>

We have presented \fs, a Mathematica package, which generates fast and
modular spectrum generators for any user specified SUSY model.  \fs is
distributed with a large number of predefined models for the CMSSM,
NMSSM, USSM, \ESSM, MRSSM etc., which can be generated immediately
without any editing.  In particular the CMSSM and NMSSM spectrum
generators constitute a fast and reliable alternative to the existing
publicly available spectrum generators, Softsusy, SPheno and
NMSPEC.

We have described how the generated source code can be influenced at
two different levels: The \mathematica level where the user provides a
model file, and the C++ level where the generated objects can be
easily exchanged, extended, modified and reused.  This provides great
flexibility for creating custom spectrum generators for both the most
common and most extraordinary models.  We have demonstrated these
features in detailed examples for the NUHMSSM, right handed neutrinos
and on adding three loop RGEs and two loop matching for the strong
gauge coupling.

The generated code has extensively tested against Softsusy, and
additional tests have been carried out for non-minimal models, the
\ESSM and MRSSM.  Speed tests have also been performed against
Softsusy, SPheno and SPheno-like MSSM code generated by SARAH,
demonstrating that \fs runs faster than all three.

As a result \fs enables fast exploitation of new SUSY models with high
precision and reliability.
